%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jingyi Bu's Curriculum Vitae
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Jonah Bu} % Your name
\address{(852)~$\cdot$~9794 5396 \\ jingyi.bu@outlook.com} % Your phone number and email
\address{GitHub $|$ https://github.com/bujingyi} % github

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary} 

\begin{rSubsection}{}{}{}{}
\item 9+ years' AI/data science experience in healthcare, aviation and insurance.
\item 5+ years' experience of leading AI/data science teams (5-10 people on multiple sites).
\item 10+ AI/Analytics solutions launched in insurance on distribution and operation.
\item 5+ AI/Analytics solutions launched in healthcare and aviation.
\item Strong stakeholder management skills for collaboration across different departments including marketing, operation, sales, and local business units.
\item Author of the book - Machine Learning: Theory and Optimization.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{AIA Group}{Nov 2018 - Now}{Associate Director, Data Science}{Mar 2022 - Now, Hong Kong}
\item Leading Analytics \& Insights team in AIA Group Distribution to optimize, standardize, and deliver the core AI and data analytics function across all distribution channels including agency, partnership distribution, digital platform distribution, and corporate solution.
\item Managing and supporting AIA local BUs on solutioning, developing, and implementing AI/data analytics use cases for distribution to achieve the business targets.
\item Supporting AIA local BUs developing the analytics strategic roadmaps.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{}{}{Senior Manager, Data Science}{Mar 2020 - Feb 2022, Hong Kong}
\item Lead Analytics \& Insights team in AIA Group Distribution to drive the delivery of AI/data analytics use cases across the four channels for all AIA markets.
\item Play a key role in the engagement of multiple teams to connect channels in Distribution, data science team in Technology, and business teams in Local BUs.
\item Support AIA local BUs developing the analytics strategic roadmaps.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{}{}{Artificial Intelligence Lead}{Nov 2018 - Feb 2020, Hong Kong}
\item Manage AIA’s three AI labs in Hong Kong (4 data scientists), Guangzhou (3 data scientists), and Ho Chi Minh City (10 AI engineers).
\item Lead AIA's exploration of where, why and how AI (cognitive and non-cognitive) may be applied to improve AIA's customer experience, distribution effectiveness, business processes and operating efficiency, while maintaining regulatory compliance.
\item Play a key role in explaining AI concepts to AIA's leadership team, defining specific 'use cases' for potential adoption, and overseeing the integration of those as appropriate into the business to create measurable impact.
\item Champion the selective launch and implementation of AI projects across the 18 Asia Pacific markets that make up the AIA Group.
\item Propose and define AIA's AI roadmap and priorities, set the direction for future technology investments in the AI field.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{GE}{Jun 2016 - Nov 2018}{Data Science Team Lead, Staff Data Scientist}{Shanghai}
\item Establish and lead data science team to explore and apply modern data analysis methods in traditional industries.
\item Participate in global projects and build solid connection between local and global data science groups.
\item Define, formulate, and develop strategies for China team's technical growth.
\item Standardize and optimize data analysis process for GE China to continuously improve efficiency and stability.
\item Cooperate and collaborate with business team to develop new customers for GE China.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Philips Research}{Apr 2013 - Jun 2016}{Scientist}{Shanghai}
\item Build disease risk models including high risk pregnancy identification, cardiovascular disease risk predication etc.
\item Apply big data analytics in Healthcare.
\item Develop data-driven and knowledge-based clinical decision support systems for Philips global markets.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Project}

%------------------------------------------------

\begin{rSubsection}{AI Powered \& Analytics Driven Agency Development Solution}{}{AIA Group Distribution, Mar 2020 - Present}{}
\item Design and develop Group level solution to support all key steps in AIA agent career development path including recruitment, training, promotion, and retention by leveraging multiple data sources e.g. aptitude test, behavior, performance etc.
\item Localized solutions have gone live in multiple markets: recruitment solution in Thailand and Vietnam; training solution in Thailand; promotion solution in Malaysia and Thailand; MDRT solution in Singapore and Malaysia; retention solution in China.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Data-driven Customer Journey for Partnership Distribution \& Digital Platform Distribution}{}{AIA Group Distribution, Nov 2020 - Present}{}
\item Collaborate with Group Marketing team on the creation of data-driven customer journey for PD (Bancassurance) and DPP (a completely new channel established in 2021) including customer acquisition, lead generation, lead nurturing, lead qualification, and seller/agent matching for lead conversion.   
\item Apply the cutting-edge technologies such as reinforcement learning based recommender system to build personalized marketing content / product recommendation engine for AIA customers.
\item Continuously supporting local BUs on the improvement of data-driven customer journeys in Hong Kong, Thailand, Malaysia, Korea, and the Philippines. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Implementation of Data-driven Underwriting for Bancassurance}{}{AIA Group Distribution, Nov 2020 - Present}{}
\item Collaborate with Group Operation team to implement the data-dirven underwriting (DDUW) which leverages the customer data from banks to predict a customer's underwriting risk to enhance the customer journey by minimizing the number of underwriting questions while increasing the maximum sum assured offered.
\item Tailor and localize DDUW solution developed by reinsurer to fit local BUs' requirements based on banks' data availabilities.
\item Tailored solutions launched in Korea, Thailand, and Vietnam.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Selected Analytics Use Cases for Corporation Solution}{}{AIA Group Distribution, Nov 2020 - Present}{}
\item Propose and deliver analytics use cases to drive the expension of CS business in multiple markets including Tailand, Hong Kong, China, Malaysia, and Singapore by CS agent profiling, IVS customer propensity modelling, and IVS customer pre-underwriting scoring.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{AI-powered Underwriting Engine for AIA Philam}{}{AIA Group Technology \& Operation, Dec 2018 - Feb 2020}{}
\item Delivered AI solution to replace the traditional manual underwriting procedure with a 60,000 times faster processing speed by transcending rule-based automation and using superior cognitive automation.
\item Designed and developed simulation method to translate rules into AI models without historical data for new product release and existing rule updates.
\item The solution went live in Feb 2020 and won Digital Transformer and Information Visionary categories at the prestigious IDC Digital Transformation Awards 2020.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Airlines Inventory Management with Reinforcement Learning}{}{GE, Sep 2017 - Nov 2018}{}
\item Designed and developed an intelligent solution to automate inventory management process such as parts replenishment, allocation, and rellocation to optimize the stock level and turnover rate. 
\item Proposed and implemented multiple AI solutions including heuristic search, DQN, PPO, SAC trained with a distributed TensorFlow framework in a gym-like environment to emulate the real world scenario.
\item Solution went live in China Eastern Airlines.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Analytics Based Maintenance}{}{GE, Jun 2016 - Jan 2017}{}
\item Built condition-based maintenance solutions that monitors the condition of assets through sensor devices for GE's aircraft engine series by a combination of a bunch of ML models handling different parts of flying cycles.
\item Main model components include regression models for component-level distress ranking prediction, and stacking models to ensemble multiple component-level regression models for engine-level removal prediction.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Cloud Based Patient Follow-up and Rehab Management Solutions}{}{Philips, Aug 2015 - Jun 2016}{}
\item Self health management solution for patients during recovery stage after cardiovascular surgery by connecting patients at homes with AI assistant and doctors in hospitals.
\item Developed user classification models to detect potential paying customers or the users who can benefit from the solution.
\item Designed and developed the knowledge base enabling the functionality of clinical decision support of the system.
\item Product launched in China.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Mobile Obstetrical Monitoring}{}{Philips, Jun 2014 - Jul 2015}{}
\item Low-cost and easy-to-use obstetrical monitoring solution for primary care in undeveloped area in Philips markets.
\item Developed risk predication models for pregnant woman on the early detection of hypertension in pregnancy and pre-eclampsia.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Intelligent Test Suite}{}{Philips, Apr 2013 - Dec 2013}{}
\item Low-cost and easy-to-use primary care solution for general practitioners by integrating sphygmomanometer, oximeter, and pulse wave velocity meter into one portable suite powered by intelligent algorithms running in backend.
\item Rebuild disease risk models on four-year hypertension, eight-year diabetes, and ten-year cardiovascular diseasesfrom literature study.
\item Design and implement knowledge base to deliver personalized recommendations.
\end{rSubsection}

%------------------------------------------------
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Shanghai Jiao Tong University} \hfill {\em 2010 - 2013} \\ 
M.S. in Neuroscience \\
Overall GPA: 2.61/3.0 | top 10\%

{\bf Shanghai Jiao Tong University} \hfill {\em 2006 - 2010} \\ 
B.S. in Biomedical \& Medical Engineering \\
Overall GPA: 3.7/4.3 | top 10\%

\end{rSection}

%----------------------------------------------------------------------------------------
% PUBLICATION & PATENT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications \& Patents}
%------------------------------------------------

\begin{rSubsection}{}{}{}{}
\item \textbf{Jingyi Bu}, Chunqi Shi. Machine Learning: Theory and Optimization. ISBN: 9787302517184, 2019.
\\
\item \textbf{Jingyi Bu}, Hao Li, Hai-Qing Gong, Pei-Ji Liang, Pu-Ming Zhang. Gap Junction Permeability Modulated by Dopamine Exerts Effects on Spatial and Temporal Correlation of Retinal Ganglion Cells' Firing Activities. in Journal of Computational Neuroscience, 2013.
\\
\item \textbf{Jingyi Bu}, Ning Lan. An Improved Multi-Channel Cortical Recording and Stimulation System. International Convention on Rehabilitation Engineering \& Assistive Technology, p. 98-101, 2010.
\\
\item Wang Jin and \textbf{Bu Jingyi}. An Apparatus and Method for Evaluating Multichannel ECG Signals. WO2015052609A1.16/04/2015
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Projects}

% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Artificial Intelligence & Data-Driven, Knowledge-Based \\
% Predictive Modeling & Deep Learning, Reinforcement Learning, Classic Machine Learning \\
% Problem Solving & Multivariate Time Series, Decision Process, Decision Support \\
% Computer Languages & Python, TensorFlow
% \end{tabular}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
