%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jingyi Bu's Curriculum Vitae
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{卜晶祎} % Your name
\address{(852)~$\cdot$~9794 5396 \\ jingyi.bu@outlook.com} % Your phone number and email
\address{GitHub $|$ https://github.com/bujingyi} % github

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary} 

\begin{rSubsection}{}{}{}{}
\item 8+ years' AI/data science experience in Healthcare and Insurance.
\item 4+ years' experience of leading AI/Data Science teams.
\item Author of the book - Machine Learning: Theory and Optimization.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{AIA Group}{Nov 2018 - Present}{Artificial Intelligence Lead}{Hong Kong}
\item Lead AIA's exploration of where, why and how AI (cognitive and non-cognitive) may be applied to improve AIA's customer experience, distribution effectiveness, business processes and operating efficiency, while maintaining regulatory compliance.
\item Play a key role in explaining AI concepts to AIA's leadership team, defining specific 'use cases' for potential adoption, and overseeing the integration of those as appropriate into the business to create measurable impact.
\item Champion the selective launch and implementation of AI projects across the 18 Asia Pacific markets that make up the AIA Group.
\item Propose and define AIA's AI roadmap and priorities, set the direction for future technology investments in the AI field.
\item Establish intellectual and commercial leadership for AIA in AI for Insurance.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{GE}{Jun 2016 - Nov 2018}{Data Science Team Lead, Staff Data Scientist}{Shanghai, China}
\item Establish and lead data science team to explore and apply modern data analysis methods in traditional industries.
\item Lead/participate in global projects and build solid connection between local and global data science groups
\item Plan, monitor, and review the results of China team's local projects.
\item Coach, counsel, and discipline team members; design individual technical/career development plan for each team member.
\item Define, formulate, and develop strategies for China team's technical growth.
\item Standardize and optimize data analysis process for GE China to continuously improve efficiency and stability.
\item Cooperate and collaborate with business team to develop new customers for GE China.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Philips Research Healthcare}{Apr 2013 - Jun 2016}{Scientist}{Shanghai, China}
\item Disease risk modeling including high risk pregnancy identification, cardiovascular disease risk predication etc.
\item Healthcare big data analytics.
\item Data-driven and knowledge-based clinical decision support.
\item Knowledge management.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Project}

%------------------------------------------------

\begin{rSubsection}{UNICORN: Agency AI-assisted Recruitment for AIA Thailand}{}{AIA, Jul 2020 - Present}{}
\item Enhanced the interview questionnaires in iRecruitment by importing a more sophisticated aptitude test to more comprehensively and accurately assess the candidates. 
\item Developing an AI solution to reduce human intervention for screening and to increase in average productivity of new agents by identifying high potential candidates and being more assertive in the recruitment.  
\item Designed and proposed Azure solutions for model deployment (will be the first use case on Azure Machine Learning environment in AIA).
\item Planned go-live date is in Jan 2021.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{FUSION: Philam AI underwriting for AIA Philippines}{}{AIA, Dec 2018 - Feb 2020}{}
\item Designed AI solution to fully replace existing rule-based underwriting process.
\item Led data science team in building models on different categories of mannually processed cases including free text, claim history, etc. for increasing straight through processing rate.
\item Proposed simulation method to translate rules into AI models without any historical data for new product release and existing rule updates.
\item Built online envolving loop to continuously increase STP rate.
\item Proved technical feasibility by a four-week POC.
\item Led 3rd-part vendors to design the software architecture and to implement the new system. 
\item The new underwriting engine went live in Feb 2020.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Agency AI solution for AIA China}{}{AIA, Nov 2018 - Dec 2019}{}
\item Built agent retention prediction model based on performance and behaviour tracking.
\item Developed agent risk detection AI solution to replace the legacy rule-based system.
\item Led data science team in building both classic machine learning models with handcrafted feature engineering and deep learning models on raw multivariate time series data e.g. weekly performance or behaviour tracking records.
\item Interpreted and explained the model results to AIA China leadership team with business values.
\item Worked closely with local IT team to integrate the models into AIA China's legacy workflow.
\item Designed and proposed Cloud solution for model deployment on Ali Cloud in China.
\item Supported AIA China in vendor selection for AI virtual agency trainers.
\item Helped AIA China build up AI capability and establish data science team by defining the roles and responsibilities, referring talents, and interviewing candidates.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Predictive system maintenance for AIA China}{}{AIA, Mar 2019 - Sep 2019}{}
\item Identify error producing nodes of AIA China's IT systems and predict issue resolve time for newly raised incidents by modelling on free text contained system log files.
\item Plan and organize a Heckfest with Microsoft Azure team to have a quick result.
\item Evaluate the suitability and applicability of Azure for AIA. 
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Airline Inventory Management with Reinforcement Learning}{}{GE, Sep 2017 - Nov 2018}{}
\item Designed and developed a gym-like environment to emulate the real world scenario.
\item Proposed and implemented multiple AI solutions including heuristic search, DQN, PPO.
\item Developed a distributed TensorFlow framework to train the model.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Engine Health Monitoring and Management}{}{GE, Jun 2016 - Nov 2018}{}
\item Forecasting model: LSTM Accepter/Transducer architecture + residual analysis.
\item Classification model: multi-channel CNN + resampling strategy.
\item Embeding model: LSTM encoder-decoder architecture + classic machine learning models.
\item Generative model: GAN + data augmentation.
\item Application scenarios: high risk aircraft engine identification; aircraft oil leakage detection and prediction; airline fleet segregation et al.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Analytics Based Maintenance}{}{GE, Jun 2016 - Jan 2017}{}
\item Built regression models (LR, CART, GBDT) for component-level distress ranking prediction.
\item Developed stacking models to ensemble multiple component-level regression models for engine-level removal prediction.
\item Lead the development of automative analytics tools for this kind of problem for global teams.
\item Facilitated GE Aviation Analytics' transition from R to Python.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Cloud Based Patient Follow-up and Rehab Management Solutions}{}{Philips, Aug 2015 - Jun 2016}{}
\item Developed user classification models to detect potential paying customers or the users who can benefit from the solution.
\item Designed and developed the knowledge base enabling the functionality of clinical decision support of the system.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Mobile Obstetrical Monitoring}{}{Philips, Jun 2014 - Jul 2015}{}
\item Developed risk predication models (LR and CART) for pregnant woman on hypertension in pregnancy and pre-eclampsia
\item Designed and implemented a random patient profile generator for physicians to validate the models.
\item Developed an Android prototype to implentent and test the models
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Personal Health Management Solution}{}{Philips, Jan 2014 - Dec 2014}{}
\item Designed the whole workflow of personal health management.
\item Developed risk predication models (Weibull) on four-year hypertension, eight-year diabetes, and ten-year cardiovascular diseases.
\item Developed recommendation delivering systems including diet and exercise according to people's risk levels.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Intelligent Test Suite}{}{Philips, Apr 2013 - Dec 2013}{}
\item Rebuild disease risk models from literature study.
\item Design and implement knowledge base to deliver personalized recommendations.
\end{rSubsection}

%------------------------------------------------
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Shanghai Jiao Tong University} \hfill {\em 2010 - 2013} \\ 
M.S. in Neuroscience \\
Overall GPA: 2.61/3.0 | top 10\%

{\bf Shanghai Jiao Tong University} \hfill {\em 2006 - 2010} \\ 
B.S. in Biomedical \& Medical Engineering \\
Overall GPA: 3.7/4.3 | top 10\%

\end{rSection}

%----------------------------------------------------------------------------------------
% PUBLICATION & PATENT SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications \& Patents}
%------------------------------------------------

\begin{rSubsection}{}{}{}{}
\item \textbf{Jingyi Bu}, Chunqi Shi. Machine Learning: Theory and Optimization. ISBN: 9787302517184, 2019.
\\
\item \textbf{Jingyi Bu}, Hao Li, Hai-Qing Gong, Pei-Ji Liang, Pu-Ming Zhang. Gap Junction Permeability Modulated by Dopamine Exerts Effects on Spatial and Temporal Correlation of Retinal Ganglion Cells' Firing Activities. in Journal of Computational Neuroscience, 2013.
\\
\item \textbf{Jingyi Bu}, Ning Lan. An Improved Multi-Channel Cortical Recording and Stimulation System. International Convention on Rehabilitation Engineering \& Assistive Technology, p. 98-101, 2010.
\\
\item Wang Jin and \textbf{Bu Jingyi}. An Apparatus and Method for Evaluating Multichannel ECG Signals. WO2015052609A1.16/04/2015
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Projects}

% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Artificial Intelligence & Data-Driven, Knowledge-Based \\
% Predictive Modeling & Deep Learning, Reinforcement Learning, Classic Machine Learning \\
% Problem Solving & Multivariate Time Series, Decision Process, Decision Support \\
% Computer Languages & Python, TensorFlow
% \end{tabular}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
